Showcase some database functionality

### 2023-06-30 indicators/insectindicators/tutorials/tutorial.Rmd
first draft, not done

Bla bla

@@

>>>>

Intro
======
Not much here yet, only some quick commands.

@@

```{r}
require(DBI)
 require(dplyr)
locations <- tbl(con,
                 Id(schema = "locations",
                    table = "localities"))

```
```{r}
locations
```
```{r}
require(sf)

locations_sf <- read_sf(con,
                 Id(schema = "locations",
                    table = "localities"))

```
```{r}
require(ggplot2)

ggplot(locations_sf) +
  geom_sf(aes(fill = habitat_type))
```

New locality function
---------

```{r}
insect_localities_sf <- get_localities()
```

```{r}
insect_localities <- get_localities(as_sf = FALSE)
```
